

\documentclass[11pt,a4paper,skipsamekey]{moderncv}      
\usepackage[english]{babel}



\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     
\usepackage{comment}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Nathan}{Corral}
\address{Frankenweg 26A 53225, Bonn}
\phone[mobile]{+49 160 9178 1918}               
\email{nathan.b.corral@gmail.com}                             


\begin{document}
	
%\recipient{To:}{Fraunhofer Institute \\ Nobelstraße 12 \\ 70569 Stuttgart}	
\recipient{To:}{Fraunhofer Institute \\ Nobelstraße 12, 70569 Stuttgart}
\date{\today}
\opening{Dear Johannes Kienle,}
\closing{Best Regards,}
%\enclosure[Attachment]{CV}
\makelettertitle

\par
I am excited to apply for the Software Engineer position for Professional Outdoor Service Robots (Req. Num. 74030) at Fraunhofer.
My aspiration is to grow into a software architect, and this role offers a clear path through contributing to the cutting-edge robotics developed by Fraunhofer.
Over the past year, I have completed two software projects that demonstrate my ability to design scalable architectures, and I am eager to bring this experience to your robotics ecosystem.

\par
I enhanced the ROS 2 Whisper open-source project by adding live transcription capabilities.
This involved restructuring the usage of Whisper.cpp (OpenAI's speech-to-text model in C++) to enable both context preservation and frequent updates.
A threaded post-processing node was then added to align and merge the text, resulting in robust performance and efficiency—skills directly applicable to maintaining the reliability of the CURT ecosystem.

\par
I designed a pipeline for deploying multiple Hugging Face models on a live camera feed, mapping model outputs to a unified label framework.
The extendable architecture supports on-demand visualization of bounding boxes and pixel masks, as demonstrated by simultaneously running DETR and Maskformer models.
This project highlights my ability to integrate complex systems—a core requirement for Fraunhofer's professional service robots.

\par
%I am well-prepared to manage Continuous Integration (CI) tasks, drawing on over 10 years of experience using Linux (Ubuntu) as my primary development environment.
I am well-prepared to manage Continuous Integration (CI) tasks, drawing on my Computer Engineering background and 10 years of experience using Linux (Ubuntu).
My prior roles have provided me with experience collaborating with interdisciplinary teams of engineers and physicists.
Additionally, as a second author on a publication in Personalized Robot Navigation, I contributed to advancements in autonomous navigation, including generating simulation-based training data and deploying these systems in real-world scenarios.

\par
Working within the CURT framework presents an exciting opportunity to contribute to the development of innovative robotic systems.
I deeply respect Fraunhofer's commitment to applied research and its transformative role in advancing robotics.
This position aligns well with my background and aspirations, and I would be honored to bring my skills to your team.

\par
Thank you for considering my application.
I look forward to the opportunity to discuss how I can contribute to Fraunhofer's projects.

\begin{comment}
	% SECOND DRAFT %
	\par
	I am excited to apply for the Software Engineer position for Professional Outdoor Service Robots (Req. Num. 74030) at Fraunhofer.  
	My asperation is to grow into a software architect, and this role offers a clear path by contributing to the cutting-edge robotics developed by Fraunhofer.  
	Over the past year, I have completed two software projects that demonstrate my ability to design scalable architectures, and I am eager to bring this experience to your robotics ecosystem.  
	
	\par
	I enhanced the ros2\_whisper open-source project by adding live transcription capabilities.  
	This involved restructuring the usage of Whisper.cpp (OpenAI's speach-to-text-model in c++), to enable both context preservation and frequent updates.  
	A threaded post-processing node was then added to align and merge the text, resulting in robust performance and efficiency.  
	Skills directly applicable to maintaining the reliability of the CURT ecosystem.  
	
	\par
	I designed a pipeline for deploying multiple Hugging Face models on a live camera feed, mapping model outputs to a unified label framework.  
	The extendable architecture supports on-avaiable visualization of bounding boxes and pixel masks, as demonstrated by simultaneously running DETR and Maskformer models.  
	This project highlights my ability to integrate complex systems—a core requirement for Fraunhofer's professional service robots.  
	
	\par
	I am well-prepared to manage Continuous Integration (CI) tasks, drawing on over 10 years of using Linux (Ubuntu) as my primary development environment.  
	My prior role in embedded systems gives me experience collaborating with interdisciplinary teams of engineers and physicists.  
	Additionally, as a second author on a publication in Personalized Robot Navigation, I contributed to advancements in autonomous navigation, including generating simulation-based training data and real-world deployment.  
	
	\par
	Working within the CURT framework presents an exciting opportunity to contribute to the development of innovative robotic systems.  
	I deeply respect Fraunhofer's commitment to applied research and its transformative role in advancing robotics.  
	This position aligns well with my background and aspirations, and I would be honored to bring my skills to your team.  
	
	\par
	Thank you for considering my application.  
	I look forward to the opportunity to discuss how I can contribute to Fraunhofer's projects.  
\end{comment}
	
	
	
	

\begin{comment}
% FIRST DRAFT %

% Intro
I am very interested in the position of Software Engineer for Professional Outdoor Service Robots at Fraunhofer.  
My aspiration is to grow into a software architect role, and this position offers an excellent opportunity to develop in that direction, particularly in AI and robotics.  
Over the last year, I have completed two software projects which demonstrate my aptitude towards software architecture development and what would make me a valuable software engineer. 
% -- or --
% Over the past year, I have completed two software projects that demonstrate my ability to contribute to this role.

% ros2 whisper
I extended the ros2\_whisper open source project by adding a feature to perform live transcription.  
This required re-structuring the project, which previously applied the wisper.cpp engine (OpenAI's speach-to-text-model in c++) over a lightly-overlapping audio data chunk.  
I made this overlap very large, for example using twenty seconds of previously seen audio and just one second of new audio data.  
This allows frequent updates while maitining context in the audio.  
I then added a post-processed node, which aligns and merges the new incomming text with what was previously seen.  
These design and architecture changes, enabled multi-threaded audio transcription.

% ros2 cv
I also authored a pipline for running multiple Hugging Face (HF) models on a live camera feed.
The HF models subscribe to the camera feed and then map their outputs to a unified label landscape. 
The visualization node subscribes to the camera image, bounding box, or pixel mask, which it then aligns and displays as a MatPlotLib animation. 
This architecture is extendable, shown by simotaniously running the DETR (bounding boxes) and Maskformer (per-pixel mask) computer vision models on a live camera feed.  

% Discuss job 
I am prepared to handle elements of Continuous Integration (CI) in this position.  
I have worked primaraly in the linux environment (ubuntu) since starting my bachlors, giving me 10 years of practice.
My work experience in Embedded Systems has given me success while working in interdisciplinary teams, in the past with Electrical Engineers and Physists. 
I strive to produced useful documentation.  % Possibly omit
In research, I have contributed (as 2nd author) to a publication in the field of Personalized Robot Navigation, which is an specification of autonomous navigtation.  % Possibly omit
In this research role, I also used a photo-realistic simiulator to generate training data. 

% Final paragraph
Working within the CURT framework would provide valuable experience in maintaining and developing software for real robots. 
I learned about Fraunhofer through my master's thesis advisor, Dr. Christian Bauckhage, and I admire the organization's leadership in applied research. 
This position aligns well with my experience and goals, and it would be an honor to join your team.

% Closing
Thank you for considering my application. 
I look forward to the opportunity to discuss how I can contribute to Fraunhofer's projects.		
\end{comment}
	
\vspace{0.5cm}
	
\makeletterclosing
	
\end{document}
