

\documentclass[11pt,a4paper,skipsamekey]{moderncv}
\usepackage[english]{babel}



\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     
\usepackage{comment}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Nathan B.}{Corral}
\address{Frankenweg 26A 53225, Bonn}
\phone[mobile]{+49 160 9178 1918}               
\email{nathan.b.corral@gmail.com}                             

\begin{document}
	\recipient{To:}{Agile Robots SE \\ Flößergasse 2 \\ Munich, Germany }
	\date{\today}
	\opening{Dear Hiring Team,}
	\closing{Best Regards,}
	%\enclosure[Attachment]{CV}
	\makelettertitle
	
	I am excited to apply for the Robotics Simulation Engineer position at Agile Robots SE.
	With a Master’s in Computer Science focused on robotics and experience in simulation environments, I am eager to contribute to advancing robotics solutions.
	
	At the Humanoid Robots Lab, I worked with iGibson, a photo-realistic simulator using a Bullet backend.
	I simulated the movement of robots along user-selected paths to gather simulated camera data for a deep learning path planning algorithm.
	The movement paths were derived from a user study where I guided participants in a Virtual Reality (VR) headset.
	In addition to this, my Master’s coursework—where I achieved top marks using CARLA (an autonomous driving simulator) and Gazebo—has prepared me well to work in industry simulation environments.
	
	Although I have yet to gain hands-on experience with Visual Components, I am eager to learn and believe my adaptability will allow me to contribute quickly at Agile Robots SE.
	My preparedness to contribute to robotics programming is demonstrated by my open-source projects in ROS 2.
	In the ROS 2 Whisper project, I showcased my software engineering background and ability to produce efficient and scalable C++ code.
	
	I am enthusiastic about the opportunity to join Agile Robots SE and help shape the future of robotics through simulation.
	I am particularly excited about the opportunity to contribute to international projects, including potential travel to Beijing, aligning with my interest in cross-cultural collaboration.
	I would welcome the opportunity to discuss how my skills and experiences align with your team’s goals.
	
	Thank you for considering my application. I look forward to the possibility of contributing to your innovative work.
	
	\begin{comment}
		
	
	
	I want to emphasize:
	 - My master focus on Robotics, where I had projects with several simulators (CARLA, )-- mention good grades so I can include my transcript.
	 - Have practical experience running iGibson in Virtual Reality (VR).  iGibson is a photo-realistic simulator with backend of Bullet -- where my task was creating the simulation data for training a deep RL agent to use for path planning.  
	 - Foundation in robotics programming as shown in my two open source projects.
	 - Although I don't currently poses experience, I am knowledgable and am egear to demonstrate progress in Visual Components
	 - I have traveled for work before, and have a Chinese Visa. So opportunities to visit Beijing are very exciting for me.
	 
	 
	
	I am excited to apply for the Robotics Simulation Engineer position at Agile Robots SE.  
	With a Master’s in Computer Science focused on robotics and experience in simulation environments, I am eager to contribute to advancing robotics solutions.
	
	At the Humanoid Robots Lab, I worked with iGibson, a photo-realistic simulator using a Bullet backend.
	I simulated the movement of robots on a user-selected path, to gather simulated camera data for a deep learning, path planning algorithm.  
	The movement path was collected through a user study, where I guided participants in a Virtual Reality (VR) headset.  
	Along with this, my Master's classes achieving top marks using CARLA (autonomous driving simulator) and Gazebo have prepared me well to work in industry simulation environments.
	
	While I have yet to gain hands-on experience with Visual Components, I am eager to learn and believe my adaptability will bring me quickly to contributing at Agile Robots SE.
	My preparedness to contribute in robotics programming are demonstrated by my open source works in ROS 2.  
	In the ROS 2 Whisper project, I show my experience as a Software Engineer and capability to produce efficient and scale-able C++ code.  
	
	I am enthusiastic about the chance to join Agile Robots SE and help shape the future of robotics through simulation.  
	I am particularly interested in the possibility of opportunity-based travel to Beijing, as I have previously performed demos in China and have a travel visa!
	I welcome the opportunity to discuss how my skills and experiences align with your team’s goals.  
	
	Thank you for considering my application. I look forward to the possibility of contributing to your innovative work.
	
	
	
	While I have yet to gain hands-on experience with Visual Components, my adaptability and eagerness to learn position me to quickly learn this tool and contribute effectively to your projects.
	
	
	Particularly my contribution in ROS 2 Whisper, demonstrates my experience in Software Engineering and capability to produce scale-able C++ code.  
	
	The ROS 2 Whisper project, shows my 
	
	Through my open source contributions in ROS 2, using 
	
	My contributions to open-source projects, including ROS 2 Whisper and a computer vision pipeline, underscore my programming foundation in Python and C++.  
	
	While I have yet to gain hands-on experience with Visual Components, my adaptability and eagerness to learn position me to quickly master this tool and contribute effectively to your projects. Additionally, my existing Chinese visa and past work-related travel experiences make the opportunity to collaborate internationally, including visits to your Beijing subsidiary, particularly exciting.
	
	I am enthusiastic about the chance to join Agile Robots SE and help shape the future of robotics through simulation. I welcome the opportunity to discuss how my skills and experiences align with your team’s goals.
	
	Thank you for considering my application. I look forward to the possibility of contributing to your innovative work.
	

	\end{comment}
	\begin{comment}
		

	I am writing to express my interest in the IT Technician position in Software Development for Artificial Intelligence (Stellen-ID: 11281) at the Institute for Artificial Intelligence in Medicine (IKIM). With a strong background in Linux systems, GPU cluster management, and AI applications in medical technology, I am confident in my ability to contribute effectively to your team.
	
	I have over a decade of experience with Linux, beginning with my Bachelor's in Computer Engineering in 2013. During my Master's studies, I frequently utilized GPU clusters to train deep learning networks and conduct research, equipping me with practical skills in managing and optimizing such resources. Additionally, I am well-versed in virtualization best practices and Docker containers, which are essential for developing and deploying complex software solutions.
	
	My personal projects, such as launching a container on Hyperspace to fine-tune a state-of-the-art computer vision network, demonstrate my initiative and ability to apply theoretical knowledge to practical scenarios. Furthermore, my work with Linux-based systems on chips, including deploying a C++ implementation of OpenAI's Whisper on the Nvidia Jetson NX Orin, showcases my proficiency in handling diverse hardware configurations.
	
	My keen interest in applying AI to medical technology is reflected in my high grade in the Master's course "Image Acquisition and Analysis in Neuroscience." This academic achievement underscores my commitment to integrating AI solutions within the medical field.
	
	I am particularly drawn to this position because it aligns perfectly with my expertise and passion for advancing medical technology through AI. I am eager to contribute to the development of sophisticated software solutions and support the technical infrastructure at IKIM.
	
	Thank you for considering my application. I look forward to the opportunity to discuss how my background and skills can benefit your team.
	\end{comment}
	\vspace{0.5cm}
	\makeletterclosing
	
	
	
	
\end{document}