
\documentclass[11pt,a4paper,skipsamekey]{moderncv}
\usepackage[english]{babel}



\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     
\usepackage{comment}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Nathan B.}{Corral}
\address{Frankenweg 26A 53225, Bonn}
\phone[mobile]{+49 160 9178 1918}               
\email{nathan.b.corral@gmail.com}                             

\begin{document}
	\recipient{To:}{Robert Bosch GmbH \\ Renningen, Germany }
	\date{\today}
	\opening{Dear Dr. Caesar,}
	\closing{Best Regards,}
	%\enclosure[Attachment]{CV}
	\makelettertitle
	
\begin{comment}
	- I am extremely interested in doing a PhD on Data-driven Self-Assessment for Multimodal Perception in Automated Driving
	
	- I have always had a passion for self-driving technologies:
 1.  Completing Computer Vision personal projects, 
 2.  Working in a start-up to innovate with state-of-the-art LiDAR technology,
 3.  Gaining experience in Embedded Systems to understand safety, real-time, and deployment details.
 4.  Working with numerous ROS / ROS 2 projects, a popular framework used in open source self-driving car software such as Autoware.
	
	- During my Master's degree, I worked towards this objective by:
  1. Supporting publications in Robotics
  2. Achieving top marks in a master's class on self-driving cars
  3. Completing my master's thesis in techniques for prediction of multiple-possible futures -- work that will spring-board me into research of multimodal fusion
	
	I am extremely interested in how this Ph.D. statement focus on real-world relevancy, specifically in the assessment of which objects in the scene which are imperative for autonomous decision-making.
	I am eager to develop metrics, implement solutions, and collaborate with other research in this context.  
\end{comment}

I am excited to apply for the PhD position in Data-driven Self-Assessment for Multimodal Perception in Automated Driving at Bosch (JobID REF217910P). This PhD aligns strongly with my academic background, practical experience, and aspirations to contribute to innovative research in autonomous driving technologies.

My passion for self-driving technologies has guided much of my professional experience.  
In my first role, I contributed to the development of an innovative LiDAR product by designing the visualization and filtering of point clouds using the C++ Point Cloud Library.  
%My background as a Computer Engineer and Embedded Systems experience give me insight into the deployment, real-time and safety considerations needed for self-driving cars. 
My background as a Computer Engineer, combined with embedded systems experience, has provided me with insight into deployment, real-time operation, and safety considerations critical for self-driving cars. 
%I have recently completed two open-source projects in the Robot Operation System (ROS 2), a popular framework used in open source self-driving car software such as Autoware. 
Additionally, I recently completed two open-source projects using the Robot Operating System (ROS 2), a widely adopted framework in self-driving car software such as Autoware. 
%The objective of this work to design a Computer Vision pipeline for deploying multiple state-of-the-art models simultaneously underlines my practical experience in self-driving car software.
The objective of this work—to design a computer vision pipeline capable of deploying multiple state-of-the-art models simultaneously—highlights my practical experience with software for autonomous vehicles.

During my master’s degree, I deepened my understanding of AI and robotics with a focus on applications in autonomous driving.
%During my master's degree, I deepened my fundamental understanding of AI and robotics, with clear objectives for how it can be used in autonomous vehicles.  
%As a student assistant, I contributed to an IROS publication in personalized path planning. 
As a student assistant, I contributed to an IROS publication on personalized path planning.
%My thesis introduced a novel, transformer-based architecture for probabilistic prediction which applied in both video and human pose generation, offering a foundation for research in multimodal fusion.  
My thesis introduced a novel transformer-based architecture for probabilistic prediction, which was applied to video and human pose generation, offering a strong foundation for research in multimodal fusion. 
%Earning top marks in both my thesis and a class on self-driving cars, I am prepared to begin a PhD in this domain.  
With top marks in both my thesis and a self-driving cars course, I am prepared to begin a PhD in this domain.


What excites me most about this position is its focus on improving real-world relevance by assessing the importance of objects in autonomous decision-making.  
Developing metrics and self-supervised methods that bridge training metrics with operational performance is a fascinating challenge.  
%I am motivated to tackle this through collaboration with a diverse and dynamic team while contributing to Bosch’s tradition of excellence in innovation.
I am eager to contribute to this effort by developing innovative solutions and collaborating with Bosch’s diverse and dynamic research team, continuing the company’s tradition of excellence in innovation.

Thank you for considering my application. I would be honored to contribute to your research and look forward to the opportunity to discuss this role further.


	\vspace{0.5cm}
\makeletterclosing




\end{document}